\chapter{Introduction}\label{chap:introduction}

The primary objective of this dissertation is to establish that knot Floer homology detects the \textit{granny knot} $T_{2,3} \# T_{2,3}$, the connect-sum of two right-handed trefoil knots. While knot Floer homology is known to detect the unknot \cite{OS-genus}, the trefoil \cite{Ghi08}, and the cinquefoil \cite{Reinoso2023}, the detection of $T_{2,3} \# T_{2,3}$ is, to our knowledge, the first detection result for a composite knot.

\section{Summary of Results}

Our main result is the following detection theorem:

\begin{theorem} \label{thm:main_detection}
Let $K \subset S^3$ be a knot. If there is an isomorphism of bigraded vector spaces
\[
\widehat{HFK}(K; \mathbb{F}) \cong \widehat{HFK}(T_{2,3} \# T_{2,3}; \mathbb{F})
\]
over the field $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$, then $K$ is isotopic to $T_{2,3} \# T_{2,3}$.
\end{theorem}

The Alexander polynomial of $T_{2,3} \# T_{2,3}$ is the square of the Alexander polynomial of the trefoil, which, combined with the rank of $\widehat{HFK}$, dictates a highly specific grading distribution. The complexity of the proof lies in rigorously eliminating all other knots that possess this homological profile.

\subsection{From Topology to Dynamics}

Our strategy to prove Theorem \ref{thm:main_detection} exploits the fact that knot Floer homology detects both the genus and fiberedness of a knot \cite{Ni07, Juh08}. The connect-sum $T_{2,3} \# T_{2,3}$ is a fibered knot of genus two, and this information is recorded directly in the top Alexander grading of $\widehat{HFK}(T_{2,3}\#T_{2,3})$. Consequently, any knot $K$ satisfying the hypothesis of Theorem \ref{thm:main_detection} must also be a genus-two fibered knot. 

This fundamental observation allows us to translate the topological problem of knot classification into a dynamical one involving the mapping class group. A genus-two fibered knot is determined by its monodromy, a surface homeomorphism $h \colon \Sigma_2^1 \to \Sigma_2^1$ of the genus-two fiber, which fixes the boundary. The knot Floer homology of $K$ constrains this monodromy in two powerful ways:
\begin{enumerate}
    \item \textbf{Homological constraint:} The Alexander polynomial of $K$ is determined by the Euler characteristic of $\widehat{HFK}$. Thus any hypothetical knot sharing the same knot Floer homology as that of $T_{2,3}\# T_{2,3}$ must share the same Alexander polynomial:
    \[
    \Delta_K(t) = \Delta_{T_{2,3}\# T_{2,3}}(t) = (t^2 - t + 1)^2.
    \]
    Thus any monodromy of such a hypothetical knot must induce this Alexander polynomial on homology.
    \item \textbf{Fixed-point constraint:} The work of Ghiggini \cite{Ghi08}, and independently of Ni \cite{Ni07}, shows that the number of fixed points of the monodromy of a fibered knot is constrained by the next-to-top Alexander grading of knot Floer homology. This directly requires $h$ to have a specific number of fixed points.
\end{enumerate}


\subsection{The Dynamical Obstruction}
By the Nielsen-Thurston classification, a surface homeomorphism is either periodic, reducible, or pseudo-Anosov. These, in turn, correspond to cases in which the knot is a torus knot, a satellite knot, or a hyperbolic knot, respectively.

Assuming a hypothetical knot $K$ satisfies the assumptions of Theorem \ref{thm:main_detection}, we systematically evaluate the cases where $K$ is assumed to be a torus knot, a satellite knot, and a hyperbolic knot. 

The torus knot case is immediate: the Alexander polynomials of the torus knots $T_{n,m}$ are known, and none coincides with that of $K$.

For the satellite knot case, we employ the classification of Thurston reducing systems. Schubert's formula for the Alexander polynomial of a satellite knot drastically restricts the potential companions and patterns to be trefoil knots. By analyzing the minimal reducing curves on the genus-two fiber, we systematically demonstrate that any non-trivial satellite construction contradicts the known properties of $K$ (e.g., fractional Dehn twist coefficients and $L$-space contact invariants), leaving only the composite sub-case.

\subsection{Eliminating the Hyperbolic Case}

The hyperbolic case is the technical heart of the dissertation. To analyze it, we descend the genus-two monodromy of $K$ to a braid mapping class on the marked disk via the \textbf{Birman-Hilden correspondence}. The key geometric fact is that the hyperelliptic involution $\iota$ is central in the mapping class group $\mathrm{Mod}(\Sigma_2^0)$, so every monodromy on the closed genus-two surface commutes with $\iota$ and descends through the quotient $\Sigma_2^0 \to \Sigma_2^0/\iota \cong S^2_{0,6}$, branched over six points. Beginning with the pseudo-Anosov representative $\phi_h \colon \Sigma_2^1 \to \Sigma_2^1$ of the monodromy of $K$ (which has exactly one interior fixed point $z$), we cap off the boundary $\partial \Sigma_2^1$ with a disk to obtain a pseudo-Anosov map $\hat{\phi}_h \colon \Sigma_2^0 \to \Sigma_2^0$ on the closed surface, with two fixed points $\{z, p\}$ swapped by $\iota$. Descending through the involution yields a pseudo-Anosov map $\phi_b \colon S^2_{0,6} \to S^2_{0,6}$ with a single non-marked fixed point $r$, the common image of $z$ and $p$. A real blow-up at $r$ then produces a pseudo-Anosov map $\phi_\beta \colon D^2 \to D^2$ on the six-marked disk, whose mapping class $\beta \in \mathrm{Mod}(D_6)$ we refer to as the \emph{disk braid} associated to $K$. The canonical lift of $\beta$ to the genus-two surface with two boundary components $\Sigma_2^2$ (the double cover of $D^2$ branched over the six marked points) is fixed-point-free in its interior, by construction. We develop this correspondence in detail in Chapter \ref{chap:preliminaries}, Section \ref{section:Birman-Hilden}.

Having reduced the topological classification problem on $S^3$ to a dynamical question about a pseudo-Anosov 6-braid whose lift is fixed-point-free, we now bring the theory of train tracks to bear. The Euler-Poincar\'{e} formula restricts $\beta$ to one of finitely many admissible singularity strata, each specified by the prong structure of the invariant foliations of $\phi_\beta$. Within each stratum, $\beta$ may be analyzed via the dynamics of its action on train tracks; however, the state space of such train tracks is in general too large for feasible analysis. Producing such an enumeration is a long-standing problem in topological dynamics: in his foundational paper on estimating the entropy of braids, Los \cite{LosAlgorithm} explicitly called for the development of a generalized, algorithmic method to construct exhaustive folding automata for train tracks on punctured disks, noting that ad-hoc constructions were a major bottleneck in dynamical classifications.

In response to this, we introduce the \texttt{autofolder} algorithm. This computational tool takes as input a stratum of mapping classes and exhaustively generates the complete directed graph of standard train tracks connected by elementary folding operations.

\begin{theorem}\label{thm:autofolder_main}
The \texttt{autofolder} algorithm provides a complete, finite classification of all standard train tracks and their valid elementary folds for any specified stratum of pseudo-Anosov braids on the $n$-punctured disk.
\end{theorem}

In particular, for each admissible stratum on the 6-marked disk, the \texttt{autofolder} outputs a finite list of standard train tracks with the property that every pseudo-Anosov 6-braid in that stratum is carried by one of the tracks on the list. This list serves as the starting point for our subsequent case analysis.

Although the \texttt{autofolder} is developed here as the computational backbone for the hyperbolic case of Theorem \ref{thm:main_detection}, the algorithm operates on arbitrary strata of the marked disk and stands as an independent contribution to the field of low-dimensional topology and topological dynamics. We discuss these broader applications in Section \ref{subsec:dilatation_enumeration_intro}.

With the \texttt{autofolder} in hand, we eliminate the hyperbolic case as follows. For each admissible stratum we generate the complete folding automaton; by the carrying theorem of Ko-Los-Song \cite{SongEntropy}, every pseudo-Anosov 6-braid in that stratum is carried by one of the finitely many standard train tracks appearing as its vertices. Whenever a stratum carries an interior singularity of at least two prongs, the refinement of Farber-Reinoso-Wang \cite{farber2024fixed} applies: every such braid is in fact carried by a \emph{jointless} standard track. Their tight-splitting operation --- the inverse of the elementary folds recorded by the automaton --- removes the joints from any standard track, so we may discard every track carrying a joint and reduce each such stratum to a short, explicit list of jointless standard tracks.

The obstructions we then impose are conditions not on the braids in the abstract, but on the induced \emph{train-track maps} $f_\beta \colon \tau \to \tau$ that these tracks carry --- equivalently, on the edge-image words of $f_\beta$ and the transition matrix $M(f_\beta)$ they determine. Each translates the requirement that the canonical lift $\phi_\Phi \colon \Sigma_2^2 \to \Sigma_2^2$ be interior fixed-point-free into a combinatorial condition on $f_\beta$: the Trace Lemma forces $\operatorname{tr} M(f_\beta) = 0$, which in the jointless setting means that no real edge incident to a marked monogon occurs in its own image; and the Absorption Obstruction, a consequence of the injectivity of the surface homeomorphism inducing $f_\beta$, forbids any edge-image from being absorbed into the cone spanned by two adjacent edge-images at a switch. We carry out the resulting enumeration in full: for every jointless track in each such stratum we exhaustively generate the train-track maps $f_\beta$ consistent with the track's combinatorics and test each one against both obstructions, either eliminating it or recording the parametric braid family to which it belongs. This program yields the following positive classification of the pseudo-Anosov 6-braids whose canonical lift to the genus-two surface with two boundary components $\Sigma_2^2$ is interior fixed-point-free:

\begin{theorem}\label{thm:fpf_classification}
Let $\beta \in \mathrm{Mod}(D_6)$ be a pseudo-Anosov 6-braid whose canonical lift $\phi_\beta \colon \Sigma_2^2 \to \Sigma_2^2$ is fixed-point-free in its interior. Then the singularity type of $\beta$ lies in one of the five admissible strata
\[
(2; 1^4, 2^2; \emptyset),\quad (4; 1^6; \emptyset),\quad (2; 1^6; 4),\quad (3; 1^6; 3),\quad (2; 1^6; 3^2).
\]
In the orientable strata $(2; 1^4, 2^2; \emptyset)$, $(4; 1^6; \emptyset)$, and $(2; 1^6; 4)$, the invariant foliations of $\phi_\beta$ on $\Sigma_2^2$ are orientable. In the non-orientable strata $(3; 1^6; 3)$ and $(2; 1^6; 3^2)$, $\beta$ or $\beta^{-1}$ is conjugate, up to a power of the full twist $\Delta^2$, to a member of one of finitely many explicit braid families. These families are enumerated in Appendices \ref{app:candidate_braids_candelabra}--\ref{app:candidate_braids_track_17}.
\end{theorem}

The three orientable strata are eliminated at once: an orientable invariant foliation would force the dilatation of $\phi_\beta$ to appear as a real root of $\Delta_{T_{2,3} \# T_{2,3}}(t) = (t^2-t+1)^2$, a polynomial with no real roots, so no pseudo-Anosov braid can inhabit these strata (Chapter \ref{chap:stratoriented}). For the two non-orientable strata, the candidate families remain; we evaluate their reduced homological action matrices and apply the homological filter.

\begin{theorem} \label{thm:homological_elimination}
None of the fixed-point-free pseudo-Anosov mapping classes generated by the standard train tracks in the admissible strata induce both an Alexander polynomial equal to $\Delta(t) = (t^2-t+1)^2$ and a 3-manifold (the underlying space of the associated open book) that is an integer homology sphere.
\end{theorem}

\begin{corollary}\label{cor:hyperbolic_elimination}
No hyperbolic knot $K \subset S^3$ satisfies $\widehat{HFK}(K; \mathbb{F}) \cong \widehat{HFK}(T_{2,3} \# T_{2,3}; \mathbb{F})$ as bigraded vector spaces over $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$.
\end{corollary}

Combined with the elimination of the periodic case (corresponding to torus knots, cf.\ the Alexander polynomial check above), Corollary \ref{cor:hyperbolic_elimination} together with the Nielsen-Thurston trichotomy forces the monodromy of $K$ to be \textit{reducible}.

\subsection{Eliminating the Satellite Case}

Having ruled out the torus and hyperbolic cases, $K$ must be a satellite knot. Schubert's formula for the Alexander polynomial of a satellite knot constrains the structure of the satellite decomposition:
\[
\Delta_K(t) \;\doteq\; \Delta_{P(U)}(t) \cdot \Delta_C(t^w),
\]
where $C$ is the companion knot, $P$ is the pattern (with winding number $w$), and $P(U)$ is the pattern realized in the unknot. The constraint $\Delta_K = (t^2 - t + 1)^2$, together with the requirement that both $C$ and $P(U)$ be fibered, forces the pattern $P(U)$ to be a trefoil, the companion $C$ to be a trefoil, and the winding number to be $|w| = 1$.

The geometric content of the satellite structure is then captured by the Thurston reducing system on the genus-two fiber: the canonical reducing curves divide the fiber into pieces with restricted geometric types. Following the framework of Baldwin and Sivek, the outermost piece of this decomposition has one of two topological types, leading to two cases:

\begin{itemize}
    \item \textbf{Case A (pair of pants):} The Baldwin-Sivek classification yields either a composite knot or a $(p,q)$-cable knot; a cable knot has winding number at least two, contradicting $|w| = 1$, so $K$ is composite. The only composite genus-two fibered knot consistent with $\Delta_K = (t^2-t+1)^2$ is a connect-sum of two trefoils.
    \item \textbf{Case B (genus-one piece):} The outer monodromy is either periodic or pseudo-Anosov. The periodic sub-case forces $K$ to be a cable knot whose winding number contradicts $|w| = 1$; the pseudo-Anosov sub-case is eliminated by a fractional-Dehn-twist-coefficient analysis using the Hedden-Mark bound and the Honda-Kazez-Mati\'{c} right-veering criterion applied to the $L$-space contact invariant.
\end{itemize}

The satellite case therefore reduces to a connect-sum of two trefoils:

\begin{corollary}\label{cor:satellite_elimination}
If $K \subset S^3$ is a non-trivial satellite knot with 
\[
\widehat{HFK}(K; \mathbb{F}) \cong \widehat{HFK}(T_{2,3} \# T_{2,3}; \mathbb{F})
\]
as bigraded vector spaces over $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$, then $K$ is isotopic to a connect-sum of two trefoils.
\end{corollary}

It remains to resolve the chirality of the two trefoil summands. The candidates are $T_{2,3} \# T_{2,3}$ (the granny knot, homochiral), $T_{2,3} \# \overline{T}_{2,3}$ (the square knot, heterochiral), and $\overline{T}_{2,3} \# \overline{T}_{2,3}$ (the mirror granny). All three share the same Alexander polynomial $(t^2 - t + 1)^2$ and the same total $\widehat{HFK}$ rank, but their bigraded $(M, A)$ supports differ. Mirroring a knot reverses both gradings, $(M, A) \mapsto (-M, -A)$; the square knot is amphichiral and so has a centrally symmetric support, while the granny and the mirror granny have supports that are central reflections of one another. The three supports are therefore distinct, and the bigraded isomorphism in the hypothesis of Theorem \ref{thm:main_detection} selects exactly one of them, namely $T_{2,3} \# T_{2,3}$. This completes the proof of Theorem \ref{thm:main_detection}; we discuss the chirality-resolution aspect further in Section \ref{sec:applications}.


\subsection{A Partial Detection Theorem for the $(2,1)$-Cable}

Beyond the granny knot, another natural target within the satellite class is the $(2,1)$-cable of the right-handed trefoil, $C_{2,1}(T_{2,3})$. This is a genus-two fibered satellite knot with Alexander polynomial
\[
\Delta_{C_{2,1}(T_{2,3})}(t) \;=\; \Delta_{T_{2,3}}(t^2) \;=\; t^4 - t^2 + 1,
\]
which differs from the granny's $(t^2-t+1)^2$, so the cable is not a candidate for $K$ in Theorem~\ref{thm:main_detection}. Both $C_{2,1}(T_{2,3})$ and the granny knot are \emph{almost L-space knots} in the sense of Baldwin and Sivek \cite{BaldwinSivek2024}: the cable is realized as a $(2, 4g-3)$-cable of the L-space knot $T_{2,3}$, and Binns \cite{Binns2023} showed that all such cables are almost L-space knots. Binns further showed that $T_{2,3} \# T_{2,3}$ is the unique composite almost L-space knot \cite{Binns2023}.

It is therefore natural to ask: does $\widehat{HFK}$ itself detect $C_{2,1}(T_{2,3})$? The same machinery developed for the granny detection --- the \texttt{autofolder} algorithm, tight splitting, the Trace Lemma, the Absorption Obstruction, and homological filtering --- can be applied to the cable target Alexander polynomial $t^4 - t^2 + 1$. This analysis dispatches the torus and satellite cases entirely, but the homological filter is less effective at the cable target than at the granny target: a small number of candidate braid families survive both filters at certain non-negative integer parameter values. We thus obtain the following partial result:

\begin{theorem}\label{thm:cable_detection_partial_intro}
Let $K \subset S^3$ be a knot such that
\[
\widehat{HFK}(K; \mathbb{F}) \cong \widehat{HFK}(C_{2,1}(T_{2,3}); \mathbb{F})
\]
as bigraded vector spaces over $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$. Then either $K$ is isotopic to $C_{2,1}(T_{2,3})$, or $K$ is hyperbolic and the disk braid associated to its monodromy under the Birman-Hilden correspondence (cf.\ Chapter \ref{chap:preliminaries}, Section \ref{section:Birman-Hilden}) belongs to one of an explicitly enumerated finite list of parametric families.
\end{theorem}

The residual hyperbolic candidates are tabulated in Appendix \ref{app:cable_residual_families}, and avenues for closing the gap are discussed in Section \ref{sec:cable_residual_discussion}. As an immediate corollary that is fully proved, we have:

\begin{corollary}\label{cor:cable_nonhyperbolic_detection_intro}
Knot Floer homology detects $C_{2,1}(T_{2,3})$ among non-hyperbolic knots: any non-hyperbolic knot $K$ with $\widehat{HFK}(K) \cong \widehat{HFK}(C_{2,1}(T_{2,3}))$ as bigraded vector spaces is isotopic to $C_{2,1}(T_{2,3})$.
\end{corollary}
\section{Applications}
\label{sec:applications}

In this section, we discuss the topological and geometric implications of our main result, Theorem \ref{thm:main_detection}, which establishes that knot Floer homology detects the connect-sum of two right-handed trefoil knots, $T_{2,3} \# T_{2,3}$ (the granny knot). We also address the implications of Theorem \ref{thm:cable_detection_partial_intro}, our partial detection result for the satellite knot $C_{2,1}(T_{2,3})$ (the $(2,1)$-cable of the right-handed trefoil).

These results contribute to the classification of genus-two fibered knots and to the rigidity theory of \textit{almost L-space knots} in the sense of Baldwin and Sivek.

\subsection{Botany of Genus-Two Fibered Knots}

Following the framework of Hedden and Watson \cite{HeddenWatson2018}, the central organizing questions of knot Floer homology in any given genus split into two complementary problems:
\begin{itemize}
    \item \emph{Geography:} which bigraded groups arise as $\widehat{HFK}(K)$ for some knot $K \subset S^3$?
    \item \emph{Botany:} given a bigraded group $V$ that does arise, which knots $K$ satisfy $\widehat{HFK}(K) \cong V$?
\end{itemize}
Detection results are precisely positive botany results: they assert that a particular bigraded group is realized by a unique knot. The two results in this dissertation, Theorems \ref{thm:main_detection} and \ref{thm:cable_detection_partial_intro}, are botany results in genus two, the same setting addressed by Reinoso \cite{Reinoso2023} for the cinquefoil $T_{2,5}$.

Genus-two fibered knots in $S^3$ fall into three Nielsen-Thurston classes: torus, satellite, and hyperbolic. The torus case is fully resolved by Reinoso's detection of $T_{2,5}$ and its mirror, the only non-trivial genus-two fibered torus knots in $S^3$. The hyperbolic case remains open --- no genus-two hyperbolic fibered knot is currently known to be detected by $\widehat{HFK}$. Theorems \ref{thm:main_detection} and \ref{thm:cable_detection_partial_intro} of this dissertation address the satellite class in two complementary sub-cases: the granny knot (composite) and the cable $C_{2,1}(T_{2,3})$ (prime). Together with Reinoso's torus result, these constitute the first systematic progress on the botany problem for genus-two fibered knots, leaving the hyperbolic class as the principal open frontier.

\subsection{The Granny as the Unique Composite Almost L-Space Knot}

A knot $K \subset S^3$ is termed an \textit{L-space knot} if there exists an integer $n$ with $|n| \geq 2g(K) - 1$ such that $S^3_n(K)$ is an L-space---a rational homology sphere $Y$ with the simplest possible Heegaard Floer homology, satisfying $\dim \widehat{HF}(Y) = |H_1(Y; \mathbb{Z})|$. 

Generalizing this notion, Baldwin and Sivek define a knot $K$ to be an \textit{almost L-space knot} if $K$ is not itself an L-space knot and there exists an integer $n$ with $|n| \geq 2g(K) - 1$ such that
\[
\dim \widehat{HF}(S^3_n(K)) = |n| + 2,
\]
i.e., large Dehn surgeries on $K$ yield 3-manifolds with Heegaard Floer homology of next-to-minimal rank \cite{BaldwinSivek2024}. Both the granny knot and the cable $C_{2,1}(T_{2,3})$ are almost L-space knots \cite{Binns2023}, and natural topological constraints --- compositeness, primeness within a given satellite pattern, fixed Alexander polynomial --- often force a knot in this class to be uniquely determined. Our detection results combine cleanly with such structural constraints.

\begin{itemize}
    \item \textbf{The granny knot.} Binns has shown that $T_{2,3} \# T_{2,3}$ is the unique composite almost L-space knot \cite{Binns2023}. Consequently, Theorem \ref{thm:main_detection} implies that $\widehat{HFK}$ detects the unique composite almost L-space knot.
    
    \item \textbf{The cable $C_{2,1}(T_{2,3})$.} Corollary \ref{cor:cable_nonhyperbolic_detection_intro} provides the first non-trivial detection result by $\widehat{HFK}$ for an almost L-space knot beyond the L-space-knot torus class: any non-hyperbolic knot with $\widehat{HFK}$ matching that of $C_{2,1}(T_{2,3})$ is $C_{2,1}(T_{2,3})$ itself.
\end{itemize}

Combining Binns' uniqueness theorem with Theorem \ref{thm:main_detection}, we obtain the following corollary:

\begin{corollary}\label{cor:detect_unique_composite_almost_lspace}
Knot Floer homology detects the unique composite almost L-space knot.
\end{corollary}

\subsection{Enumerating Pseudo-Anosovs of Bounded Dilatation}
\label{subsec:dilatation_enumeration_intro}

Beyond its role in the proof of Theorem \ref{thm:main_detection}, the \texttt{autofolder} algorithm provides a tool for the systematic enumeration of pseudo-Anosov mapping classes by dilatation. By the framework of Ko, Los, and Song \cite{SongEntropy}, every pseudo-Anosov braid in a given stratum is conjugate to one represented by a closed cycle in the folding automaton for that stratum, and the dilatation of the braid is the spectral radius of the product of transition matrices recorded along the cycle. The \texttt{autofolder} algorithm explicitly produces this automaton, with the transition matrix attached to every edge, making the dilatation of any cycle directly computable from the automaton data.

A bound on the dilatation translates, via Perron-Frobenius theory, into a bound on the length of cycles that need to be examined. Indeed, the transition matrix associated to a cycle is a product of the elementary folding matrices recorded along its edges, so longer cycles produce matrices with larger entries. Since each elementary folding matrix contributes a fixed amount to the total entry sum, the entry sum $|M|$ of the transition matrix of a cycle grows linearly in the cycle length. The Perron-Frobenius inequality
\[
\lambda^n \geq |M| - n + 1,
\]
valid for any $n \times n$ Perron-Frobenius matrix with leading eigenvalue $\lambda > 1$ (\cite[Lemma~3.1]{HamSong2007}), then converts an upper bound $\lambda \leq \lambda_0$ into an upper bound on $|M|$, and thereby into an upper bound on the cycle length. Consequently, for any fixed stratum $\mathcal{S}$ and any $\lambda_0 > 1$, the enumeration of pseudo-Anosov mapping classes in $\mathcal{S}$ with dilatation at most $\lambda_0$ reduces to traversing a finite portion of the \texttt{autofolder} automaton. This is the same strategy used by Ham and Song to determine the minimum dilatation of pseudo-Anosov 5-braids \cite{HamSong2007}, carried out by hand for that single stratum; the \texttt{autofolder} framework turns this approach into an algorithmic computation applicable to any stratum.

This procedure is particularly well-suited to investigating questions about fixed-point structure and dilatation in specific strata, an area which has seen recent activity from a number of directions \cite{AougabFuterTaylor2025}.

\section{Outline of the Chapters}

This dissertation is structured to systematically eliminate topological candidates for the knot $K$, moving from algebraic algorithms to geometric dynamics. 

In \textbf{Chapter \ref{chap:preliminaries}}, we provide the necessary background on knot Floer homology, the Birman-Hilden correspondence, and the Nielsen-Thurston classification of surface homeomorphisms. We rigorously establish the bounds placed on the geometric monodromy by the knot Floer homology of $T_{2,3} \# T_{2,3}$, and dispatch the torus knot case via an elementary Alexander polynomial check.

In \textbf{Chapter \ref{chap:train tracks}}, we develop the theory of train tracks on punctured disks and surfaces with boundary, including standard and jointless train tracks, the Birman-Hilden lift, and the Trace Lemma which encodes fixed-point information of the lifted monodromy.

In \textbf{Chapter \ref{chap:stratoriented}}, we introduce the primary technique for ruling out mapping classes based on the orientability of their invariant foliations. We show that for three specific strata, the lifted invariant foliations on $\Sigma_2^2$ are orientable, forcing the dilatation of the monodromy to appear as a real root of $\Delta_{T_{2,3} \# T_{2,3}}(t) = (t^2 - t + 1)^2$. Since this polynomial has no real roots greater than $1$, these strata are eliminated.

In \textbf{Chapter \ref{chap:folding_automata}}, we detail the theoretical construction of folding automata and our algorithmic realization. We prove Theorem \ref{thm:autofolder_main} and demonstrate how the \texttt{autofolder} algorithm explicitly generates the finite, exhaustive list of standard train tracks in each stratum required for the dynamical classification.

In \textbf{Chapter \ref{chap:tight_splitting}}, we introduce the tight-splitting operation, which prunes the \texttt{autofolder}'s output to a small set of jointless standard train tracks carrying the same pseudo-Anosov maps. We prove that this reduction terminates (Theorem \ref{thm:splitting_termination}) and that, up to conjugation and mirroring, every pseudo-Anosov braid in the non-orientable strata is carried by one of finitely many terminal tracks --- the Candelabra in the stratum $(3;1^6;3)$, and six tracks in $(2;1^6;3^2)$.

In \textbf{Chapter \ref{chap:stratatraintrackanalysis}}, we deploy this machinery to eliminate the remaining non-orientable strata. Using the reduced list of jointless tracks, the Trace Lemma, and the Absorption Obstruction, we enumerate all valid train track maps on the 6-marked disk and apply homological filters to rule out every hyperbolic candidate. 

In \textbf{Chapter \ref{chap:satellite}}, having eliminated all torus and hyperbolic knot candidates, we analyze the remaining reducible (satellite) case. We utilize Schubert's formula and Thurston reducing systems to definitively prove that $K$ must be the connect-sum of two right-handed trefoil knots.

In \textbf{Chapter \ref{chap:proof_of_main_theorem}}, we assemble the preceding results into a complete proof of Theorem \ref{thm:main_detection}, including the chirality discharge that distinguishes the granny knot from the square knot and from the mirror granny knot via the bigraded structure of $\widehat{HFK}$.

In \textbf{Chapter \ref{chap:cable_detection}}, we adapt the framework to the $(2,1)$-cable of the trefoil. We prove the partial detection theorem for $C_{2,1}(T_{2,3})$ (Theorem \ref{thm:cable_detection_partial}), enumerating the residual list of hyperbolic candidates that survive the homological filters and discussing avenues for closing the resulting gap.

Finally, in \textbf{Chapter \ref{chap:conclusion}}, we summarize the principal results, discuss broader implications, and identify directions for future research, including the extension of the autofolder framework to higher-genus detection problems and to Khovanov-homology analogues.
