\chapter{Detection of the (2,1)-Cable of the Trefoil}
\label{chap:cable_detection}

In this chapter, we apply the machinery developed in Chapters \ref{chap:train tracks}--\ref{chap:satellite} to the detection problem for $C_{2,1}(T_{2,3})$, the $(2,1)$-cable of the right-handed trefoil. Our principal result is a partial detection theorem: we show that any knot $K \subset S^3$ with $\widehat{HFK}(K) \cong \widehat{HFK}(C_{2,1}(T_{2,3}))$ is either isotopic to $C_{2,1}(T_{2,3})$ or, if hyperbolic, must arise from one of an explicitly enumerated finite list of candidate braid families that survive both the homology-sphere filter and the Alexander polynomial filter.

\section{Statement of the Result}\label{sec:cable_main_theorem}

Let $C = C_{2,1}(T_{2,3})$ denote the $(2,1)$-cable of the right-handed trefoil knot $T_{2,3}$.  This is a genus-two fibered satellite knot in $S^3$ with Alexander polynomial
\[
\Delta_C(t) = t^2 - 1 + t^{-2},
\]
which after clearing denominators becomes the cyclotomic polynomial
\[
t^2 \cdot \Delta_C(t) = t^4 - t^2 + 1 = \Phi_{12}(t).
\]

The complete bigraded knot Floer homology of $C_{2,1}(T_{2,3})$ over $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$, computed using the SnapPy implementation of Sz\'{a}b\'{o}'s algorithm \cite{szabo2017knotfloercalculator}, is shown in Figure~\ref{fig:hfk_cable}. The total rank is $7$, with two Alexander gradings ($A = \pm 1$) carrying rank $2$ and the remaining three ($A = 0, \pm 2$) carrying rank $1$.

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=0.8]
  % Grid
  \draw[step=1, gray!30, very thin] (-2.5,-4.5) grid (2.5,0.5);

  % Axes
  \draw[->, thick] (-2.7,0) -- (2.9,0) node[right] {$A$};
  \draw[->, thick] (0,-4.7) -- (0,0.9) node[above] {$M$};

  % Axis labels
  \foreach \a in {-2,-1,1,2} {
    \node[below=2pt] at (\a,-4.5) {\small$\a$};
  }
  \foreach \m in {-4,-3,-2,-1} {
    \node[left=2pt] at (-2.5,\m) {\small$\m$};
  }

  % HFK generators: (A, M) with multiplicity
  \node[circle, fill=black, inner sep=2pt] at (2, 0)  {};
  \node[above right] at (2, 0) {\small$1$};

  \node[circle, fill=black, inner sep=2pt] at (1, 0) {};
  \node[above right] at (1, 0) {\small$1$};

  \node[circle, fill=black, inner sep=2pt] at (1,-1) {};
  \node[above right] at (1,-1) {\small$1$};

  \node[circle, fill=black, inner sep=2pt] at (0,-1) {};
  \node[above right] at (0,-1) {\small$1$};

  \node[circle, fill=black, inner sep=2pt] at (-1,-2) {};
  \node[above right] at (-1,-2) {\small$1$};

  \node[circle, fill=black, inner sep=2pt] at (-1,-3) {};
  \node[above right] at (-1,-3) {\small$1$};

  \node[circle, fill=black, inner sep=2pt] at (-2,-4) {};
  \node[above right] at (-2,-4) {\small$1$};

  % Two diagonals: delta = 1 and delta = 2
  \draw[blue, dashed, thick] (-2.5,-3.5) -- (1.5,0.5);
  \node[blue] at (1.7,-0.3) {\small$\delta=1$};
  \draw[red, dashed, thick] (-2.5,-4.5) -- (2.5,0.5);
  \node[red] at (2.7,-0.3) {\small$\delta=2$};
\end{tikzpicture}
\caption{The bigraded knot Floer homology
$\widehat{HFK}(C_{2,1}(T_{2,3}); \mathbb{F}_2)$. Each dot represents a
generator at bigrading $(A, M)$; the integer beside each dot is the rank
$\dim_{\mathbb{F}}\widehat{HFK}_M(C_{2,1}(T_{2,3}), A)$. The top Alexander
grading is $2$, of rank $1$, so this knot is fibered of genus $2$. Two
generators sit at bigrading $(0, -1)$ and $(1, 0)$ on the diagonal $\delta = A - M = 1$;
the remaining five lie on the diagonal $\delta = 2$, so the knot fails
to be thin. In particular, the next-to-top Alexander grading $A = 1$
has rank $2$, exceeding the L-space bound, so $C_{2,1}(T_{2,3})$ is not
an L-space knot. The Ozsv\'{a}th-Szab\'{o} concordance invariant is
$\tau(C_{2,1}(T_{2,3})) = 2$, the Alexander grading of the unique generator
in Maslov grading $0$ along the $\delta = 2$ diagonal.}
\label{fig:hfk_cable}
\end{figure}

The knot $C$ is an almost L-space knot in the sense of Baldwin and Sivek \cite{BaldwinSivek2024}.

\begin{remark}[Derivation of $\tau(C_{2,1}(T_{2,3})) = 2$]\label{rem:tau_cable_derivation}
The value $\tau(C_{2,1}(T_{2,3})) = 2$ asserted above can be read directly from the bigraded rank table of Figure~\ref{fig:hfk_cable}, but it also admits a structural derivation independent of the explicit computation. Hom's cabling formula for the $\tau$-invariant \cite{HomCabling2014} gives
\[
\tau(K_{p,q}) \;=\; p \cdot \tau(K) \;+\; \frac{(p-1)(q-1)}{2}
\]
whenever the companion $K$ satisfies $\varepsilon(K) = 1$, where $\varepsilon$ denotes Hom's epsilon invariant. The right-handed trefoil $T_{2,3}$ is an L-space knot, and every L-space knot satisfies $\varepsilon = 1$; combined with $\tau(T_{2,3}) = 1$, the formula gives
\[
\tau(C_{2,1}(T_{2,3})) \;=\; 2 \cdot \tau(T_{2,3}) \;+\; \frac{(2-1)(1-1)}{2} \;=\; 2 \cdot 1 \;+\; 0 \;=\; 2.
\]
In particular, $\tau(C_{2,1}(T_{2,3})) = g(C_{2,1}(T_{2,3})) = 2$, so by Hedden's characterization of strong quasipositivity for fibered knots \cite{Hedden2010}, the cable $C_{2,1}(T_{2,3})$ is strongly quasipositive. This identity $\tau = g$ is used in Section~\ref{subsec:cable_hyperbolic} to invoke the right-veering monodromy property in the hyperbolic case.
\end{remark}

\begin{theorem}[Partial cable detection]\label{thm:cable_detection_partial}
Let $K \subset S^3$ be a knot such that
\[
\widehat{HFK}(K; \mathbb{F}) \cong \widehat{HFK}(C_{2,1}(T_{2,3}); \mathbb{F})
\]
as bigraded vector spaces over $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$. Then one of the following holds:
\begin{enumerate}
    \item $K \cong C_{2,1}(T_{2,3})$, or
    \item $K$ is hyperbolic, and the disk braid $\beta \in \mathrm{Mod}(D_6)$ associated to the monodromy of $K$ via the Birman-Hilden correspondence --- obtained by capping off the pseudo-Anosov monodromy on $\Sigma_2^1$ to $\Sigma_2^0$, descending to the marked sphere $S^2_{0,6}$, and blowing up the canonical fixed point --- belongs to one of the finitely many parametric families enumerated in Appendix \ref{app:cable_residual_families}.
\end{enumerate}
\end{theorem}

The residual hyperbolic candidates of case (2) constitute the obstruction to a complete detection theorem. We discuss this gap and possible avenues for closing it in Section \ref{sec:cable_residual_discussion}.

\begin{remark}
Theorem \ref{thm:cable_detection_partial} should be contrasted with the complete detection result for $T_{2,3}\#T_{2,3}$ established in Theorem \ref{thm:main_detection}. The granny knot analysis succeeds because every candidate braid family with $|\det(I-A_{\text{red}})|=1$ either has the wrong characteristic polynomial outright or admits no non-negative integer parameter values yielding the granny target $(t^2-t+1)^2$. The cable target $\Phi_{12}(t) = t^4 - t^2 + 1$ is comparatively well-aligned with several of the parametric polynomials produced by the candidate braids on the disk, leaving a small but non-trivial residue of unresolved cases.
\end{remark}

\section{Initial Reductions and the Trichotomy}\label{sec:cable_trichotomy}

Let $K$ satisfy the hypotheses of Theorem \ref{thm:cable_detection_partial}. The Euler characteristic computation gives $\Delta_K(t) = t^2 - 1 + t^{-2}$, so $K$ has genus exactly $2$. By the fiberedness criterion of Ni \cite{Ni07}, $K$ is fibered. Let
\[
h \colon \Sigma_2^1 \to \Sigma_2^1
\]
denote its monodromy.

By Thurston's classification of knots, $K$ falls into one of three geometric categories. We treat each in turn.

\subsection{The torus knot case}\label{subsec:cable_torus}

If $h$ is periodic, then $K$ is a torus knot $T_{p,q}$. Every torus knot is an L-space knot (or the mirror of one), and L-space knots satisfy
\[
\dim_{\mathbb{F}} \widehat{HFK}(K, a) \le 1 \quad \text{for all } a \in \mathbb{Z}.
\]
However, the rank table of Figure~\ref{fig:hfk_cable} shows that
\[
\dim_{\mathbb{F}} \widehat{HFK}(C, 1) = 2,
\]
and the hypothetical isomorphism $\widehat{HFK}(K) \cong \widehat{HFK}(C)$ would force $\dim_{\mathbb{F}} \widehat{HFK}(K, 1) = 2$ as well. Hence $K$ is not a torus knot.

\subsection{The satellite knot case}\label{subsec:cable_satellite}

Suppose $h$ is reducible, so that $K$ is a satellite knot.  We invoke the classification framework established in Chapter \ref{chap:satellite}: by Schubert's formula and the Hirasawa-Murasugi-Silver criterion \cite{HirasawaMurasugiSilver2008}, any genus-two fibered satellite knot has one of two structures, classified by the type of the canonical reducing system.

\begin{lemma}\label{lem:cable_satellite_classification}
If $K$ is a fibered genus-two satellite knot with Alexander polynomial $\Delta_K(t) = t^2 - 1 + t^{-2}$, then $K \cong C_{2,1}(T_{2,3})$.
\end{lemma}

\begin{proof}
We adapt the satellite analysis of Chapter \ref{chap:satellite}; as the genus computation below shows, the reducing-system dichotomy resolves differently for the cable target than for the granny target.  Schubert's formula gives
\[
\Delta_K(t) = \Delta_{P(U)}(t) \cdot \Delta_C(t^w),
\]
where $P$ is the pattern (with winding number $w$), $C$ is the companion, $P(U)$ is the satellite of the unknot by the same pattern. Both $C$ and $P(U)$ are fibered \cite[Corollary 4.15, Proposition 5.5]{BZ03}.

Since $K$ is fibered, the algebraic winding number is non-zero, so $|w| \geq 1$. Furthermore, because $C$ is a fibered knot, the maximum degree of its symmetrized Alexander polynomial strictly equals its Seifert genus $g(C)$. Consequently, $\Delta_C(t^w)$ is a nontrivial symmetric Laurent polynomial of maximum degree $|w| \cdot g(C) \geq 1$.

Now $\Delta_K(t) = t^2 - 1 + t^{-2}$ has maximum degree $2$ as a symmetric Laurent polynomial. The factorization above forces $|w| \cdot g(C) + \deg \Delta_{P(U)} = 2$, where $\deg$ denotes the maximum degree of the symmetrized polynomial. Since both factors have non-negative degree, we obtain three cases.

\textbf{Case $|w| = 2$, $g(C) = 1$, $\Delta_{P(U)} = 1$.} Then $\Delta_C(t^2) = t^2 - 1 + t^{-2}$ forces $\Delta_C(t) = t - 1 + t^{-1}$, the Alexander polynomial of the trefoil; as $C$ is a genus-one fibered knot, $C \cong T_{2,3}$. Since $\Delta_{P(U)} = 1$ and $P(U)$ is fibered, $P(U)$ is the unknot, so $g(P(U)) = 0$.

We determine the reducing-system configuration. Schubert's geometric genus inequality (Theorem~\ref{thm:schubert}) gives $2 = g(K) \geq g(P(U)) + m \cdot g(C) = m$, while $m \geq |w| = 2$ always; hence the wrapping number is $m = |w| = 2$. Moreover, by Lemma~\ref{lem:outer_genus_equals_pattern_genus} the outermost piece satisfies $g(\Sigma_0) = g(P(U)) = 0$. A planar outermost surface occurs only in Case A of Lemma~\ref{lem:satellite_CaseACaseB}, where $\Sigma_0$ is a pair of pants; equivalently, the fiber meets the satellite torus in $m = 2$ curves. (Case B is impossible here, as it requires $g(\Sigma_0) = 1$.)

A pair of pants admits no pseudo-Anosov homeomorphism, so the outer map $\phi_0$ is periodic, and Baldwin--Sivek's classification (Proposition~\ref{prop:knottracesprop}) applies: $K$ is a torus knot, a composite knot (with $\Sigma_0$ planar), or a $(p,q)$-cable knot. The torus case is excluded in Section~\ref{subsec:cable_torus}. A composite knot of genus two is a connect-sum of two genus-one fibered knots, each a trefoil or figure-eight; the three possible products of their Alexander polynomials have $t^{\pm 1}$-coefficients $-2$, $4$, and $-6$, none equal to the vanishing $t^{\pm 1}$-coefficient of $\Delta_K(t) = t^2 - 1 + t^{-2}$, so the composite case is excluded. Hence $K$ is a cable knot, and the pattern $P$ is a torus-knot pattern $T_{a,b}$ with $P(U) = T_{a,b}$ and winding number $a$. From $|w| = 2$ we obtain $a = 2$, and from $P(U) = T_{2,b}$ being the unknot we obtain $|b| = 1$. Therefore $P$ is the $(2,1)$-cable pattern, the companion is $C \cong T_{2,3}$, and $K \cong C_{2,1}(T_{2,3})$ up to chirality.

The identification $|b| = 1$ also follows independently of the unknottedness of $P(U)$: for $|b| \geq 3$, the torus knot $T_{2,b}$ is an L-space knot, and cabling preserves the L-space property over the L-space companion $T_{2,3}$ \cite{HeddenCableLSpace}, which would force $K$ to be an L-space knot, contradicting the rank-$2$ Alexander grading of Figure~\ref{fig:hfk_cable}.

\textbf{Case $|w| = 1$, $g(C) = 2$, $\Delta_{P(U)} = 1$.} Then $\Delta_C(t) = t^2 - 1 + t^{-2}$ and $P(U)$ is the unknot (the only fibered knot with trivial Alexander polynomial). By Hirasawa-Murasugi-Silver \cite{HirasawaMurasugiSilver2008}, a fibered satellite $K = P(C)$ with winding number $1$ and $P$ isotopic to the core (which is forced when $P(U)$ is the unknot and $|w| = 1$) satisfies $K \cong C$; that is, the satellite operation is trivial. This contradicts our assumption that $K$ is a non-trivial satellite.

\textbf{Case $|w| = 1$, $g(C) = 1$, $\deg \Delta_{P(U)} = 1$.} Then $\Delta_C(t)$ has degree $1$ and $\Delta_{P(U)}(t)$ has degree $1$, with their product equal to $t^2 - 1 + t^{-2}$. Symmetric Laurent polynomials of degree $1$ have the form $at + b + at^{-1}$, so their product has constant coefficient sum $2a_1 a_2 + b_1 b_2$. The polynomial $t^2 - 1 + t^{-2}$ has zero $t^{\pm 1}$ coefficients, forcing $a_1 b_2 + a_2 b_1 = 0$. Combined with the coefficient of $t^2$ being $a_1 a_2 = 1$, we obtain $a_1 = a_2 = \pm 1$ and $b_1 = -b_2$. Then the constant term is $2 - b_1^2 = -1$, so $b_1^2 = 3$, which has no integer solution. Hence this case is excluded.

This concludes the proof: the only allowable satellite structure is Case 1, giving $K \cong C_{2,1}(T_{2,3})$.
\end{proof}

\subsection{The hyperbolic knot case}\label{subsec:cable_hyperbolic}

Suppose $h$ is pseudo-Anosov, so that $K$ is hyperbolic. The rank table of Figure~\ref{fig:hfk_cable} shows $\dim_{\mathbb{F}} \widehat{HFK}(K, 1) = \dim_{\mathbb{F}} \widehat{HFK}(C, 1) = 2$, so by the theorem of Ni-Ghiggini-Spano (Theorem~\ref{theorem:ni-fibered}), the pseudo-Anosov representative $\phi_h$ has at most $1$ interior fixed point on $\Sigma_2^1$. The Farber-Reinoso-Wang classification \cite{farber2024fixed} then rules out the case of zero interior fixed points: the cinquefoil $T_{2,5}$ is the only fibered genus-two knot in $S^3$ whose monodromy is fixed-point-free, and its Alexander polynomial $t^2 - t + 1 - t^{-1} + t^{-2}$ differs from $\Delta_C(t) = t^2 - 1 + t^{-2}$, so $K \neq T_{2,5}$. Hence $\phi_h$ is not fixed-point-free and has exactly one interior fixed point.

Before invoking the capping-off construction, we verify that its hypotheses are met for $K$, even though $K$ is not thin. The cable $C = C_{2,1}(T_{2,3})$ has $\tau(C) = 2 = g(C)$ (see Figure~\ref{fig:hfk_cable}); since $\tau$ and $g$ are read off from the bigraded $\widehat{HFK}$ structure, the isomorphism $\widehat{HFK}(K) \cong \widehat{HFK}(C)$ forces $\tau(K) = 2 = g(K)$ as well. By Hedden \cite{Hedden2010}, a fibered knot $K \subset S^3$ satisfying $\tau(K) = g(K)$ is strongly quasipositive, and its open book decomposition supports the standard tight contact structure $\xi_{\mathrm{std}}$ on $S^3$. By Honda-Kazez-Mati\'c \cite{honda2007right}, the monodromy of an open book supporting a tight contact structure is right-veering. Hence $\phi_h$ is right-veering and the fractional Dehn twist coefficient satisfies $c(\phi_h) \geq 0$; since $\phi_h$ is pseudo-Anosov (in particular, irreducible), Honda-Kazez-Mati\'c further yield $c(\phi_h) > 0$. This is the hypothesis on the monodromy required by the capping-off construction, and so the construction applies to $K$ in the same form as it does in the granny case --- the absence of thinness (in the sense of $\widehat{HFK}$ supported on a single diagonal) plays no role in the capping-off argument.

By the capping-off construction (Proposition \ref{prop:capping off}) and the Birman-Hilden correspondence (Section \ref{section:Birman-Hilden}), this monodromy descends to a 6-braid mapping class $\beta \in \mathrm{Mod}(D_6)$ on the marked disk, whose canonical lift to the genus-two surface with two boundary components $\Sigma_2^2$ is fixed-point-free in its interior. The Euler-Poincar\'{e} stratum analysis from Chapter \ref{chap:preliminaries} then restricts $\beta$ to one of the five admissible strata
\[
(2; 1^4, 2^2; \emptyset),\quad (4; 1^6; \emptyset),\quad (2; 1^6; 4),\quad (3; 1^6; 3),\quad (2; 1^6; 3^2).
\]

The orientability obstruction of Chapter \ref{chap:stratoriented} eliminates the three orientable strata for any target Alexander polynomial without real roots. The roots of the symmetrized cable polynomial $t^4 - t^2 + 1 = \Phi_{12}(t)$ are the primitive twelfth roots of unity $\zeta_{12}^{\pm 1}, \zeta_{12}^{\pm 5}$, none of which are real. Hence the orientable strata are excluded for the cable target as they were for the granny target.

The non-orientable strata $(3; 1^6; 3)$ and $(2; 1^6; 3^2)$ require the non-trivial train-track analysis of Chapter \ref{chap:stratatraintrackanalysis}. The same \texttt{autofolder} enumeration, tight-splitting reduction, Trace Lemma, and Absorption Obstruction all apply unchanged in the cable setting, since these geometric and combinatorial constraints depend only on the assumption that the canonical lift is fixed-point-free, which we have established above.

Therefore the same finite list of $87$ candidate braid families (across the Candelabra and the five surviving two-triangle tracks) constitutes the residual list of topological candidates for the cable monodromy.

\section{Homological Filtering for the Cable Target}\label{sec:cable_filtering}

We now apply the homological filters of Section \ref{sec:homological_filtering}, retargeted to the cable's Alexander polynomial.

\begin{lemma}\label{lem:cable_polynomial_target}
The reduced homological action $A_{\text{red}}$ associated with the cable monodromy of $K$ satisfies
\[
\det(tI - A_{\text{red}}) = t^4 - t^2 + 1 = \Phi_{12}(t).
\]
\end{lemma}

\begin{proof}
Lemma \ref{lem:capping_invariance} relates $\det(tI - A)$ on the bordered surface $\Sigma_2^2$ to the closed-surface action via $\det(tI - A) = (t-1)^2 \det(tI - A_{\text{red}})$.  Since the standard Alexander polynomial of the closed monodromy on $\Sigma_2$ equals the (cleared-denominator) Alexander polynomial $t^2\Delta_C(t) = t^4 - t^2 + 1$ of $K$, the result follows.
\end{proof}

The zero-surgery Filter 1, requiring $|\det(I-A_{\text{red}})| = 1$, is unchanged. The Alexander polynomial Filter 2 now requires
\[
\det(tI-A_{\text{red}}) \,=\, t^4 - t^2 + 1.
\]

\begin{prop}\label{prop:cable_filter_outcome}
Let $\beta$ be a candidate 6-braid from one of the $87$ families enumerated in Propositions \ref{prop:candelabra_34_braids} and \ref{prop:two_triangle_braids}.  Let $A_{\text{red}}(\beta)$ denote its reduced homological action.  Then $\beta$ satisfies both
\[
|\det(I - A_{\text{red}}(\beta))| = 1
\quad \text{and} \quad
\det(tI - A_{\text{red}}(\beta)) = t^4 - t^2 + 1
\]
at non-negative integer values of the family's parameters $k, m, j \ge 0$ if and only if $\beta$ belongs to one of the following families and parameter values:
\begin{center}
\begin{tabular}{lll}
\toprule
Track & Family & Surviving non-negative parameter values \\
\midrule
Candelabra & 16 Kieve & $(j,k,m) = (0,3,4),\ (0,7,0),\ (1,2,0)$ \\
Track 0 & 7 Briefing & infinite family of $(j,k,m)$ pairs \\
Track 0 & 8 Briefing & $(k,m) = (1,2),\ (2,1)$ \\
Track 0 & 10 Quail & infinite family of $(j,k,m)$ pairs \\
Track 0 & 13 Treasure & $(k,m) = (2,1)$ \\
Track 8 & 9 FAT & $k = 2$ \\
\bottomrule
\end{tabular}
\end{center}
All other $81$ candidate families are excluded by either Filter 1 or Filter 2 at every non-negative integer parameter value.
\end{prop}

\begin{proof}
The reduced action $A_{\text{red}}(\beta)$ is computed via the same matrices $M_1, \dots, M_5$ defined in Section \ref{sec:homological_filtering}, applied to the candidate braid words of Appendices \ref{app:candidate_braids_candelabra}--\ref{app:candidate_braids_track_17}.  We then evaluate the determinant $|\det(I-A_{\text{red}})|$ and the characteristic polynomial $\det(tI-A_{\text{red}})$ as functions of the family's parameters and check whether non-negative integer values exist for which both filters return their target values.

The complete computation, performed via the implementation of the homological filter described in Section \ref{sec:homological_filtering}, reproduces the determinant and polynomial expressions tabulated for the granny case (since these depend only on $\beta$ and not on the chosen target polynomial).  Cross-checking the polynomial against the cable target $t^4 - t^2 + 1$ then identifies the residual list above; the verdict for each individual family is recorded in Appendix \ref{app:cable_residual_families}.
\end{proof}

\section{Discussion of the Residual Hyperbolic Candidates}\label{sec:cable_residual_discussion}

The six families isolated in Proposition \ref{prop:cable_filter_outcome} represent the gap between Theorem \ref{thm:cable_detection_partial} and a complete detection result. Closing this gap requires invoking obstructions beyond the simple polynomial equality at the level of the reduced homological action. Several concrete approaches to eliminating the residual list are discussed in the Conclusion (Section \ref{sec:future_directions}, ``Closing the cable detection gap''), where they are framed alongside related future-work directions. A complete cable detection theorem along these lines is the subject of ongoing work and is not included in this dissertation.

\section{Implications for Almost L-Space Knots}\label{sec:cable_implications}

While Theorem \ref{thm:cable_detection_partial} is partial, it does suffice to establish the following corollary, which contributes to the rigidity theory of almost L-space knots.

\begin{corollary}\label{cor:cable_nonhyperbolic_detection}
Knot Floer homology detects $C_{2,1}(T_{2,3})$ among non-hyperbolic knots.  More precisely, any non-hyperbolic knot $K \subset S^3$ with $\widehat{HFK}(K) \cong \widehat{HFK}(C_{2,1}(T_{2,3}))$ as bigraded vector spaces is isotopic to $C_{2,1}(T_{2,3})$.
\end{corollary}

\begin{proof}
By Theorem \ref{thm:cable_detection_partial}, alternative (2) is excluded under the hypothesis that $K$ is non-hyperbolic, leaving alternative (1).
\end{proof}

In the language of Baldwin-Sivek, Corollary \ref{cor:cable_nonhyperbolic_detection} says that $C_{2,1}(T_{2,3})$ is rigidly identified by its $\widehat{HFK}$ within the class of torus and satellite genus-two fibered knots, complementing Theorem \ref{thm:main_detection}'s identification of $T_{2,3}\#T_{2,3}$ within the same class.
