\chapter{Conclusion and Future Directions}\label{chap:conclusion}

We have established that knot Floer homology detects the granny knot $T_{2,3}\# T_{2,3}$ as a bigraded vector space over $\mathbb{F} = \mathbb{Z}/2\mathbb{Z}$, providing the first detection result for a composite knot. Along the way, we developed the \texttt{autofolder} algorithm — a complete, algorithmic realization of the folding-automaton framework theorized by Ko, Los, and Song — and a partial detection result for the $(2,1)$-cable of the trefoil. In this concluding chapter, we summarize the principal results, discuss their broader implications, and identify directions for future research.

\section{Summary of Results}

The principal results of this dissertation are the following.

\begin{theorem}[Theorem \ref{thm:main_detection}]
Let $K \subset S^3$ be a knot. If $\widehat{HFK}(K; \mathbb{F}) \cong \widehat{HFK}(T_{2,3}\#T_{2,3}; \mathbb{F})$ as bigraded vector spaces, then $K$ is isotopic to $T_{2,3}\# T_{2,3}$.
\end{theorem}

\begin{theorem}[Theorem \ref{thm:autofolder_main}]
The \texttt{autofolder} algorithm provides a complete, finite classification of all standard train tracks and their valid elementary folds for any specified stratum of pseudo-Anosov braids on the $n$-punctured disk.
\end{theorem}

\begin{theorem}[Theorem \ref{thm:cable_detection_partial}]
Let $K \subset S^3$ be a knot with $\widehat{HFK}(K) \cong \widehat{HFK}(C_{2,1}(T_{2,3}))$ as bigraded vector spaces. Then either $K \cong C_{2,1}(T_{2,3})$, or $K$ is hyperbolic and the disk braid $\beta \in \mathrm{Mod}(D_6)$ associated to the monodromy of $K$ via the Birman-Hilden correspondence (capping off to $\Sigma_2^0$, descent to $S^2_{0,6}$, blowup at the canonical fixed point) belongs to one of finitely many parametric families enumerated in Appendix \ref{app:cable_residual_families}. In particular, $\widehat{HFK}$ detects $C_{2,1}(T_{2,3})$ among non-hyperbolic knots.
\end{theorem}

The proof strategy throughout combines three threads. First, the genus and fiberedness detection results of Ozsv\'{a}th-Szab\'{o}, Ni, and Juh\'{a}sz translate the topological classification problem into a problem about surface monodromies. Second, the Birman-Hilden correspondence descends the genus-two monodromy to a 6-braid on the disk, where train track methods become applicable. Third, the explicit machinery developed in this dissertation — the \texttt{autofolder}, tight splitting, the Trace Lemma, the Absorption Obstruction, and the homological filtering pipeline — exhaustively eliminates candidate mapping classes within each topological stratum.

\section{Direct Consequences}

\subsection{Almost L-space rigidity}

The granny knot is the unique composite almost L-space knot, by a theorem of Binns \cite{Binns2023}. Combined with our Theorem \ref{thm:main_detection}, this establishes:

\begin{corollary}
Knot Floer homology detects the unique composite almost L-space knot.
\end{corollary}

For the cable, our partial result already establishes detection within the non-hyperbolic class:

\begin{corollary}
Among non-hyperbolic knots in $S^3$, the cable $C_{2,1}(T_{2,3})$ is uniquely identified by its bigraded knot Floer homology.
\end{corollary}

These results contribute to the program of using $\widehat{HFK}$ as a detector of certain distinguished knot classes, complementing Reinoso's classification of genus-two L-space knots \sidecite{Reinoso2023}, from which $\widehat{HFK}$-detection of $T(2,5)$ follows, and Baldwin-Hu-Sivek's Khovanov-homology detection of $T(2,5)$ \sidecite{baldwin2025khovanov}.

\subsection{The autofolder as a stand-alone contribution}

The \texttt{autofolder} algorithm, while developed here in service of Theorem \ref{thm:main_detection}, is independently useful. Los \sidecite{LosAlgorithm} explicitly called for an algorithmic realization of the folding-automaton machinery to make the state space of pseudo-Anosov mapping classes tractable; the \texttt{autofolder} provides this. Beyond the specific strata analyzed in Chapters \ref{chap:stratoriented} and \ref{chap:stratatraintrackanalysis}, the algorithm operates on arbitrary strata of the marked disk and outputs the complete folding automaton.

We anticipate that the algorithm will be a useful tool for future detection problems on genus-two and higher fibered knots, for the explicit construction of pseudo-Anosov braids of small dilatation, and for the experimental investigation of singularity strata that have not yet been analyzed by hand.

\section{Future Directions}\label{sec:future_directions}

\subsection{Closing the cable detection gap}
\label{sec:closing_cable_gap}

The most immediate open problem left by this dissertation is closing the gap in Theorem \ref{thm:cable_detection_partial}: eliminating the residual finite list of candidate braid families that pass both the homology-sphere filter and the Alexander polynomial filter at non-negative integer parameter values. The six families isolated in Proposition \ref{prop:cable_filter_outcome} represent precisely this gap. Closing it requires obstructions beyond polynomial equality at the level of the reduced homological action. We outline two complementary avenues.

\paragraph{(A) Pseudo-Anosov degeneration at boundary parameter values.}
The candidate train track maps in the residual families are parametrized by integer twists. At certain parameter values --- particularly $k = 0$ or $m = 0$ --- the corresponding braid may degenerate into a non-pseudo-Anosov mapping class (periodic or reducible), in which case the topological enumeration assumption is violated. A direct check of the dilatation (Perron-Frobenius eigenvalue of the train track transition matrix) at each surviving parameter value would either confirm the braid is pseudo-Anosov or exclude that parameter from consideration. This is a strictly local refinement to the existing case analysis and would yield a smaller residual list.

\paragraph{(B) Direct knot reconstruction and $\widehat{HFK}$ comparison.}
A more ambitious avenue is to bypass the homological filter entirely and directly compute the knot corresponding to each surviving braid family, then compute its knot Floer homology and compare against the cable target. The pipeline is:
\begin{enumerate}
    \item For each candidate braid word $\beta$ and parameter assignment, close up the braid lift on $\Sigma_2^2$ to obtain a fibered three-manifold, and identify the knot component $K_\beta$ that plays the role of the candidate for our knot $K$;
    \item Use SnapPy \sidecite{SnapPy} (which handles braid closures, computes hyperbolic structures, and identifies knots from their hyperbolic invariants) to recognize $K_\beta$ as a specific knot in $S^3$;
    \item Compute $\widehat{HFK}(K_\beta)$ directly --- either from known catalogues if $K_\beta$ is identified as a tabulated knot, or via dedicated knot Floer software for novel knots --- and compare against the target $\widehat{HFK}(C_{2,1}(T_{2,3}))$, including the full bigraded structure rather than just the Alexander polynomial.
\end{enumerate}
This is in principle a complete obstruction: if $K_\beta$ is not isotopic to $C_{2,1}(T_{2,3})$, the comparison will detect it. The practical challenge is the computational handling of step (1) --- mapping from a train-track-map braid word on the disk through the Birman-Hilden lift to a concrete knot in $S^3$ that SnapPy can ingest --- which requires either careful manual reconstruction or further automation built on top of the \texttt{autofolder} infrastructure. The bigraded comparison in step (3) captures Maslov-grading information beyond the Alexander polynomial and would, in principle, resolve any residual ambiguity that the polynomial filter misses.

Either avenue, if it successfully eliminates all residual candidates, would close the gap and yield a complete cable detection theorem.

\subsection{Detection beyond genus two}

The strategy of this dissertation ---  Birman-Hilden descent to a braid on the disk, and exhaustive train-track elimination of candidate mapping classes --- extends to higher-genus fibered knots only under an important structural constraint.

In genus two, the hyperelliptic involution $\iota$ is central in the mapping class group $\mathrm{Mod}(\Sigma_2)$, so \emph{every} monodromy of a genus-two fibered knot automatically commutes with $\iota$ and therefore descends to a $(2g+2) = 6$-braid on the disk via the Birman-Hilden correspondence. For genus $g \geq 3$, the picture changes: the hyperelliptic mapping class group
\[
\mathcal{H}_g \;=\; C_{\mathrm{Mod}(\Sigma_g)}(\iota)
\]
is a \emph{proper} subgroup of $\mathrm{Mod}(\Sigma_g)$, and Birman-Hilden descent applies only to monodromies in $\mathcal{H}_g$ --- the so-called \textbf{hyperelliptic} (or \textbf{symmetric}) monodromies. Consequently, the framework developed here generalizes naturally to fibered knots of genus $g \geq 3$ \emph{whose monodromy is hyperelliptic}, but not directly to general genus-$g$ fibered knots. 

Even within the hyperelliptic class, the principal computational obstruction in genus three is the rapid growth in complexity of the train-track state space: the Euler-Poincar\'{e} stratum analysis admits substantially more strata, and the \texttt{autofolder}'s output graphs grow correspondingly. 

\subsection{Khovanov detection of the granny knot}

The detection of the granny knot by knot Floer homology raises the natural question of whether Khovanov homology detects $T_{2,3}\# T_{2,3}$ as well. Khovanov homology is currently known to detect the unknot, the two trefoils, the figure-eight, the cinquefoils $T(\pm 2,5)$, $5_2$, and the Whitehead doubles $\mathrm{Wh}^\pm(T_{2,3},2)$, but is not known to detect any composite knot. A Khovanov-side analog of Theorem \ref{thm:main_detection} would be the first such detection result.

We outline the natural strategy here, adapted from the Khovanov detection of the figure-eight knot by Baldwin, Dowlin, Levine, Lidman, and Sazdanovic \sidecite{BaldwinDowlinLevineLidmanSazdanovic2021}. The granny knot has the following relevant invariants:
\begin{itemize}
    \item $\dim_{\mathbb{Q}} \widetilde{Kh}(T_{2,3}\# T_{2,3}) = 9$, since reduced Khovanov homology is multiplicative under connect sum and $\dim_{\mathbb{Q}} \widetilde{Kh}(T_{2,3}) = 3$;
    \item $T_{2,3}\# T_{2,3}$ is thin (a connect sum of thin knots is thin);
    \item $T_{2,3}\# T_{2,3}$ is strongly quasipositive, and $\tau(T_{2,3}\# T_{2,3}) = g(T_{2,3}\# T_{2,3}) = 2$.
\end{itemize}

Let $K \subset S^3$ be a knot whose reduced Khovanov homology over $\mathbb{Q}$ is isomorphic to $\widetilde{Kh}(T_{2,3}\# T_{2,3};\mathbb{Q})$ as a bigraded vector space. The proposed argument proceeds in three steps:

\begin{enumerate}
    \item \emph{Khovanov thinness.} The bigraded isomorphism implies $K$ is thin (Khovanov-thinness is a property of the bigraded structure).

    \item \emph{Spectral sequence collapse.} Dowlin's spectral sequence \sidecite{Dowlin2024} from reduced Khovanov homology to $\widehat{HFK}$ degenerates at the $E_2$-page for thin knots, yielding
    \[
    \widehat{HFK}(K;\mathbb{Q}) \cong \widehat{HFK}(T_{2,3}\#T_{2,3};\mathbb{Q})
    \]
    as bigraded vector spaces.

    \item \emph{$\widehat{HFK}$-detection.} Theorem \ref{thm:main_detection} (extended from $\mathbb{F}_2$ to $\mathbb{Q}$ coefficients) concludes $K \cong T_{2,3}\# T_{2,3}$.
\end{enumerate}

The principal subtlety in this strategy is the extension of Theorem \ref{thm:main_detection} from $\mathbb{F}_2$ to $\mathbb{Q}$ coefficients, which requires verifying that the fixed-point obstructions used in the proof remain valid in characteristic zero. We do not pursue this in the present work.

A natural further question is whether the strategy above could be adapted to detect the \emph{square knot} $T_{2,3} \# \overline{T}_{2,3}$, which is the most prominent composite knot with the same Alexander polynomial as the granny. Here Step 3 fails: $\tau(T_{2,3} \# \overline{T}_{2,3}) = 0 \neq g(T_{2,3} \# \overline{T}_{2,3}) = 2$, so the square knot is not strongly quasipositive, and the strong-quasipositive simplifications used in the granny case fail. The square knot in fact lies in an infinite $\widehat{HFK}$-equivalence class (Subsection \ref{subsec:hfk_kh_pretzel} below), placing it genuinely beyond the reach of $\widehat{HFK}$-driven detection. Khovanov detection of the square knot would therefore require a different mechanism, and would yield the first Khovanov detection result for a composite knot.

\subsection{Knot Floer homology and Khovanov homology on the Hedden-Watson pretzel family}
\label{subsec:hfk_kh_pretzel}

The square knot $T_{2,3} \# \overline{T}_{2,3}$ is the central member of the infinite Hedden-Watson pretzel family $\{P(3,-3,2n)\}_{n\in\mathbb{Z}}$ shown in Figure \ref{fig:hedden_watson_family}. All members of this family share the same knot Floer homology and the same instanton knot Floer homology \sidecite{HeddenWatson2018,Wang2020}, with $P(3,-3,0)$ being the square knot. In the geography/botany framework of \S\ref{sec:applications}, this family is a negative botany result for genus two: the bigraded $\widehat{HFK}$ profile of the square knot is realized by infinitely many distinct knots, and consequently no positive botany result --- no detection theorem --- can ever be obtained for the square knot via $\widehat{HFK}$ alone. The natural follow-up question is whether the family itself is detectable as a collection.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
  % Top-left: n = -1
  \begin{scope}[shift={(-4.5, 4.5)}]
    \bandhighlight
    \pretzel{3}{-3}{-2}{thesisblue}
    \node[font=\bfseries] at (0, 3.45) {$P(3,\,-3,\,-2)$};
    \node[font=\itshape\small, text=black!60] at (0, -3.9) {$n=-1$};
  \end{scope}

  % Top-right: n = 0 (square knot)
  \begin{scope}[shift={(4.5, 4.5)}]
    \bandhighlight
    \pretzel{3}{-3}{0}{thesisred}
    \node[font=\bfseries] at (0, 3.45)
      {$P(3,\,-3,\,0)=T_{2,3}\,\#\,\overline{T}_{2,3}$};
    \node[font=\itshape\small, text=black!60] at (0, -3.9)
      {$n=0$ \ (square knot)};
  \end{scope}

  % Bottom-left: n = 1
  \begin{scope}[shift={(-4.5, -4.5)}]
    \bandhighlight
    \pretzel{3}{-3}{2}{thesisblue}
    \node[font=\bfseries] at (0, 3.45) {$P(3,\,-3,\,2)$};
    \node[font=\itshape\small, text=black!60] at (0, -3.9) {$n=1$};
  \end{scope}

  % Bottom-right: n = 2
  \begin{scope}[shift={(4.5, -4.5)}]
    \bandhighlight
    \pretzel{3}{-3}{4}{thesisblue}
    \node[font=\bfseries] at (0, 3.45) {$P(3,\,-3,\,4)$};
    \node[font=\itshape\small, text=black!60] at (0, -3.9) {$n=2$};
  \end{scope}
\end{tikzpicture}
\caption[The Hedden-Watson pretzel family $P(3,-3,2n)$]{%
The Hedden-Watson pretzel family $P(3,-3,2n)$, due to an unpublished observation of Rasmussen and formalized in \sidecite{HeddenWatson2018}. All four members shown above have isomorphic knot Floer homology. The member $P(3,-3,0)$ (top right) is the square knot $T_{2,3}\,\#\,\overline{T}_{2,3}$; twisting the third tangle (highlighted) by $n$ full twists yields the further members $P(3,-3,2n)$, each carrying the same $\widehat{HFK}$. This infinite family is the canonical obstruction to $\widehat{HFK}$ detection of the square knot. The analogous construction with two right-handed trefoils, $P(3,3,2n)$, fails to produce a $\widehat{HFK}$-equivalent family for the granny knot: the four-ball genus bound $|\tau(K)| \leq g_4(K)$ gives $g_4(T_{2,3} \# T_{2,3}) \geq 2$, so the granny is not slice and hence not a band sum of two unknots.}
\label{fig:hedden_watson_family}
\end{figure}

This picture raises two complementary conjectures about how $\widehat{HFK}$ and Khovanov homology interact with the family:

\begin{quote}
\textbf{Conjecture (Coarse HFK detection of the family).} \emph{If $\widehat{HFK}(K) \cong \widehat{HFK}(P(3,-3,2n))$ for some (equivalently, every) $n$, then $K = P(3,-3,2m)$ for some $m \in \mathbb{Z}$.}
\end{quote}

\begin{quote}
\textbf{Conjecture (Khovanov refinement).} \emph{The members of the family $\{P(3,-3,2n)\}_{n\in\mathbb{Z}}$ have pairwise non-isomorphic Khovanov homology.}
\end{quote}

If both conjectures hold, $\widehat{HFK}$ and Khovanov homology together detect each $P(3,-3,2n)$ as a knot: $\widehat{HFK}$ identifies membership in the family, and Khovanov refines that identification to a specific member. This would be a clean complementarity between the two invariants on a family where $\widehat{HFK}$ alone cannot suffice, being constant on the family. Both conjectures are structural questions about the interaction of $\widehat{HFK}$ and Khovanov homology, naturally raised by the existence of the Hedden-Watson pretzel family but not directly addressed by the techniques of this dissertation.

\subsection{Generalizing the autofolder}

The \texttt{autofolder} as currently implemented enumerates standard train tracks on the marked disk. Two natural extensions are:

\begin{itemize}
    \item \textbf{Closed surfaces of higher genus.}  Train track theory on closed surfaces (rather than on the disk) is well-developed, but the algorithmic enumeration is more delicate due to the absence of a canonical embedding.  An autofolder operating directly on $\Sigma_g$ would give a valuable contribution.
    \item \textbf{Activating the edge data.} The current \texttt{autofolder} outputs the vertex set of the folding automaton; the edge set, encoding standardizing braids and transition matrices, is computed by the package but not utilized in our obstruction. The dilatation-enumeration applications of this edge data are discussed in the introduction (Section \ref{subsec:dilatation_enumeration_intro}); other potential uses include the study of finer dynamical invariants of pseudo-Anosov mapping classes within each stratum.
\end{itemize}

\section{Closing Remarks}

The detection of the granny knot by knot Floer homology demonstrates that the bigraded structure of $\widehat{HFK}$ is sufficiently rich to identify a knot uniquely even in the presence of essential tori in its complement, where geometric obstructions of the hyperbolic kind are unavailable. The combination of monodromy descent via Birman-Hilden, train-track classification via the \texttt{autofolder}, and homological filtering via the characteristic polynomial of the lifted action provides a template for future detection results in low-dimensional topology.

We hope that the methods developed in this dissertation — particularly the algorithmic infrastructure for navigating the geometry of mapping class groups — will serve as a springboard for further work on the rigidity of knot invariants and the classification of pseudo-Anosov mapping classes.