\chapter*{Preface}
\label{ch:preface}
\addcontentsline{toc}{chapter}{\nameref{ch:preface}}

We show that knot Floer homology detects the connect sum of two ??-handed trefoils. This is the first and to-date only detection result in knot Floer homology of connect sums of two prime knots; and the second known detection result in knot Floer homology for knots of genus greater than one. The bulk of our work is focused on ruling out any candidate knots being hyperbolic. This involves the study of the geometry of pseudo-Anosov maps, and the theory of train tracks and folding automata of an $n$-marked disk. We construct and implement a halting algorithm that outputs the folding automaton for an $n$-marked disk, in any specified stratum. This leads to the classification of fixed-point-free pseudo-Anosov maps in all but one stratum on the genus-two surface with two boundary components. To facilitate our classification, we exhibit a family of train tracks carrying all pseudo-Anosov maps in most strata
on the $6$-marked disk. As a consequence of our proof technique, we almost completely classify genus-two, hyperbolic, fibered knots with knot Floer homology of rank 1 in
their next-to-top grading in any 3-manifold. Several corollaries follow, regarding the
Floer homology of cyclic branched covers, SU(2)-abelian Dehn surgeries, Khovanov
and annular Khovanov homology, and instanton Floer homology.


First and foremost, I would like to thank Prof. Dr.~John Baldwin for his  supervising me throughout my journey.

Secondly, to Dr.~Braeden Reinoso for proposing this as a dissertation project, and for laying the groundwork on which my entire dissertation lies on. Braeden, I consider you my unofficial co-advisor, your 


Melody! Thank you for your support Tor and Gary

My dearest friends Rafael, Ana, Nate


My mother, sister, and Steve






Charlotte, thank you for exposing me to the world of Morse theory and its many related topics.
Thank you for your advice, patience, and the weekly chats which kept me motivated through the year.

I would like to thank Prof.~Joeri Van der Veken and Dr.~François Thilmany for reading and evaluating this thesis.

I would like to thank my family for their support, giving me the opportunity to make this possible.

Lastly, Marie, thank you for the whiteboard in front of which we have spent many hours together.
It was essential for finishing this thesis.
Thank you for listening to my never ending rambles on Morse theory, proofreading my thesis, being the test subject for my presentations and for the much needed distraction.

\hfill \emph{Kevin, March 2026}
